Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-10 paper/ms.tex
Add text to introduce lsr in app

\section{LSR Variations} \label{app:lsr}
\begin{figure*}
\plotone{fig/lsr.pdf}
\caption{The local standard of rest (LSR) as a function of azimuth at the
fiducial Solar circle ($R_{\odot} = 8.2\,\kpc$). No best-fit subtraction is
performed here as we did in the case of the midplane
(Section~\ref{ssec:local_midplane}).}
\end{figure*}

>>>>

\section{LSR Variations} \label{app:lsr}
We consider the variations of the LSR as a function of azimuth at the fiducial
solar circle ($R_{\odot} = 8.2\,\kpc$). At each azimuth, $\phi$, we take the
median velocity in cylindrical coordinates of all stars within $200\,\pc$ of
the position, following \citet{2018arXiv180610564S}. No best-fit subtraction
was performed as in Figure~\ref{fig:midplane}.

\begin{figure*}
\plotone{fig/lsr.pdf}
\caption{The local standard of rest (LSR) as a function of azimuth at the
fiducial Solar circle ($R_{\odot} = 8.2\,\kpc$). No best-fit subtraction is
performed here as we did in the case of the midplane
(Section~\ref{ssec:local_midplane}).}
\end{figure*}
